PANCHANGE_data_preprocessing

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Reorganised dem summary chunks for the cohorts to make more sense.

@@

@@

```{r nbr demo summary}
if(NBR == TRUE) {
summarytools::dfSummary(
  dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```

@@

```{r glad dem head}
head(dem.raw.id)
```

```{r glad dem summary}
summarytools::dfSummary(
  dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

>>>>

```{r glad dem summary}
if(GLAD == TRUE) {
summarytools::dfSummary(
  dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```

@@

```{r edgi dem summary}
if(EDGI == TRUE) {
summarytools::dfSummary(
  dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```

@@

```{r nbr dem summary}
if(NBR == TRUE) {
summarytools::dfSummary(
  dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```

@@

```{r dem summary}
if(GLAD == TRUE | EDGI == TRUE) {
summarytools::dfSummary(
  dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
}
```
